---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

##Tracking student screen time and daily workload
This report explores student daily habits, including time spent at university, phone usage, screen time, and assignments due. The aim is to identify patterns in student workload and behaviour.

```md
```{r}
logged_data <- read_csv("https://raw.githubusercontent.com/AkashaS-cmd/Stats220/main/STATS%20220%20Form%20%28Responses%29%20-%20Form%20responses%201.csv")

latest_data <- logged_data %>%
  rename(
    hours_uni = `How many hours did you spend at university today? (round to nearest whole number)`,
    phone_pickups = `How many times did you pick up the phone during the day today? (See All App & Website Activity > Scroll down to Pick-Ups)`,
    assignments_due = `How many assignments did you have due today?(including quizzes, labs, assessments)`,
    screen_time = `What screen time range were you in today?`,
    productivity = `How productive did you feel today`
  )

mean_hours <- mean(latest_data$hours_uni, na.rm = TRUE)
mean_pickups <- mean(latest_data$phone_pickups, na.rm = TRUE)

```

On average, students spent `r round(mean_hours, 1)` hours at university.
The average number of phone pickups was `r round(mean_pickups, 1)`.

### Screen time distribution
The bar chart below shows the screen time ranges reported by students.

```{r}
latest_data %>%
  ggplot(aes(x = screen_time)) +
  geom_bar() +
  labs(
    title = "Screen time range of students",
    x = "Screen time range",
    y = "Count"
 ) +
  theme_minimal()
```

### Assignments due
The bar chart below shows how many assignments students had due that day.

```{r}
latest_data %>%
  ggplot(aes(x = factor(assignments_due))) +
  geom_bar() +
  labs(
    title = "Number of assignments due that day",
    x = "Assignments due",
    y = "Count"
 ) +
  theme_minimal()
```




